Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-10-13 tex/nusselt_paper.tex
Adding grant and allocation info; may edit depending on response from NAS.

\subsection{acknowledgements}
This work was supported by the CU/NSO George Ellery Hale Graduate Fellowship,
Juri's allocation and Ben's allocation.
We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.

>>>>

\subsection{acknowledgements}
This work was supported by the CU/NSO George Ellery Hale Graduate Fellowship
and supported by NASA LWS grant number NNX16AC92G.  Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center
with allocations (GID s1647, PI Brown; GID g26133, PI Toomre).
We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.
